A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-30 sections/model_overview/main.tex
Reword a sentence

Here, \(\alpha\) represents the ``importance'' of each objective,
where high \(\alpha\) indicates a higher weight on the proportion of lost 
individuals and smaller \(\alpha\) a higher weight on the time blocked. 
The choice of \(p_A\) and \(p_B\) rely solely on equation
\ref{eq:obj_distributor}.
Note that the current system is modelled using unobservable queues which is not
necessarily an unrealistic approach~\cite{unobservablequeue}.
However, there are several other factors that can affect the routing of the
patients that are outside the scope of this paper.
For example the distance from each hospital or even the priority level of each
patient may be a significant factor that affects the ambulance service's
decision.

>>>>

Here, \(\alpha\) represents the ``importance'' of each objective,
where high \(\alpha\) indicates a higher weight on the proportion of lost 
individuals and smaller \(\alpha\) a higher weight on the time blocked. 
The choice of \(p_A\) and \(p_B\) rely solely on equation
\ref{eq:obj_distributor}.
Note that the current system is modelled using unobservable queues which is not
necessarily an unrealistic approach~\cite{unobservablequeue}.
Another approach would be to allow the ambulance service to observe the state
of each hospital before deciding which one to join for a given individual.
There are several other factors that can affect the routing of the
patients that are outside the scope of this paper.
For example the distance from each hospital or even the priority level of each
patient may be a significant factor that affects the ambulance service's
decision.
